### 2017-10-21 paper/sections/6_results.tex
paper: fix microbenchmark section
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

%The in-house cluster has  2 dual core 2GHz processors with 8GB of RAM wh
%three daemons per object storage server (one for each disk formatted with XFS)
%and they share an SSD for the journal.  The nodes are running Ubuntu 12.04.4,
%kernel version 3.2.0-63 but all experiments run in Docker containers; this
%makes it easier to tear down and re-initialize the cluster ({\it e.g.},
%dropping the kernel cache) between experiments.

@@

%\begin{figure*}[tb]
%\centering
%\includegraphics[width=180mm]{graphs/slowdown.png}
%\caption{Compared to the \texttt{create} phase, saving and persisting
%updates (\texttt{create+save} and \texttt{create+save+persist}) experience only
%a 4.79\(\times\) and 8.66\(\times\) slowdown, in the worst case for 100K files.
%In contrast, maintaining \texttt{global} consistency is 905.70\(\times\)
%slower.  The disadvantage of decoupling the namespace is the merge phase where
%updates are applied to the metadata store (\texttt{create+apply}, resulting in a
%905.70\(\times\) slowdown for 100K files.}\label{fig:global-v-decoupled}
%\end{figure*}

\subsection{Microbenchmarks}
\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-mechanisms.png}
\caption{ [\href{https://...}{source}] Microbenchmark: performance of each
mechanism. Results are normalized to the runtime of the ``Append Client
Journal" mechanism (the runtime of writing \(n\) file creates to the client's
in-memory journal).  \label{fig:slowdown-mechanisms}}
\end{figure}

@@

Figure~\ref{fig:slowdown-mechanisms} shows the runtime of the Cudele
mechanisms for a single client creating files in the same directory, normalized
to the time it takes to write \(n\) file create updates to the client's
in-memory journal ({\it i.e.} the ``Append Client Journal" mechanism). Bars
above \(10^0\) are slower than the ``Append Client Journal" mechanism.
``Stream" is an approximation of the overhead and is calculated by subtracting
the runtime of the job with the journal turned off from the runtime with the
journal turned on.  The largest workload we tested is 100K file creates in the
same directory.  This is the maximum recommended size of a directory in CephFS;
preliminary experiments with larger directory sizes show memory problems.

{\it Poorly Scaling Data Structures:} Despite doing the same amount of
work, mechanisms that rely on poorly scaling data structures have large
slowdowns for the larger number of creates. For example, ``RPCs" which relies
on the internal CephFS directory structures, goes from a \(40\times\) slowdown
for 10K files to a \(90\times\) slowdown for 100K files. It is a well-known
problem that directory data structures do not scale when creating files in the
same directory~\cite{ren:sc2014-indexfs} and any mechanism that uses these data
structures will experience similar slowdowns. Other mechanisms that write
events to a journal ({\it e.g.} the persists, ``Volatile Apply") experience a
much less drastic slowdown because the journal data structure does not need to
be scanned for every operation. Events are written to the end of the journal without
even checking the validity ({\it e.g.}, if the file already exists for a create),
which is another form of relaxed consistency because the file system assumes the
application has resolved conflicting updates in a different way.

@@

% persist vs. save: one disk vs. many
{\it Parallelism of the Object Store:} Comparing ``Local" and ``Global
persist" demonstrates the bandwidth advantages of storing the journal in a
distributed object store. For 100K file creates, the ``Global Persist"
performance is \(1.5\times\) faster because the object store is leveraging the
collective bandwidth of the disks in the cluster. This benefit comes from the
object store itself but should be acknowledged when making decisions for the
application; the size of the object store can help mitigate the overheads of
globally persisting metadata updates.

@@

\noindent\textbf{Takeaway}: the Cudele mechanisms have overheads and costs
that can differ {\it by orders of magnitude}. Cudele gives users the ability
to compose these mechanisms based on their application's correctness
requirements and performance goals.\\

\subsection{Use Case 1: Creates in the Same Directory}
\label{use-case-1}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-strong-v-weak.png}
\caption{ [\href{https://...}{source}] Use Case 1: the RPC per metadata update
(strong consistency) has a large overhead compared to decoupled namespaces
(weak consistency.)\label{fig:slowdown-strong-weak}}
\end{figure}

Figure~\ref{fig:slowdown-strong-weak} shows the runtime of systems employing
weak and strong consistency, normalized to the runtime of the ``Append Client Journal"
mechanism (again, just creating files in the client's in-memory journal).  We
use the following compositions from the mechanisms in
Table~\ref{table:spectrum}:  Strong Consistency = ``RPCs" + ``Stream"; Strong
Consistency, No Fault Tolerance = ``RPCs"; Weak Consistency = ``Append Client Journal" +
``Local Persist"; and Weak Consistency, No Fault Tolerance = ``Append Client Journal" +
``Local Persist" + ``Volatile Apply".

% Final file system metadata states are equivalent No guarantees while
% transitioning mechanisms
We compare these semantics because the final metadata states are equivalent.
Cudele makes no guarantees during execution of the mechanisms or when
transitioning semantics -- the semantics are guaranteed {\it once the mechanism
completes}. So if servers fail during a mechanism, metadata or data may be
lost.

% DeltaFS vs. BatchFS vs. POSIX: decoupled is faster
% (5-7x) vs. (90-104x) slower
% Does not scale?
% Strong Consistency > 10X slower than Weak Consistency 
{\it Speedups of Decoupled Namespaces:} Weak consistency uses the
decoupled namespace strategy and shows up to a \(20\times\) speedup over the
traditional namespaces that use RPCs. Compared to the baseline the slowdown is
\(5-7\times\) for Strong Consistency, which emulates BatchFS and
\(90-104\times\) for Weak Consistency, which emulates DeltaFS.

% POSIX (no stream) vs. POSIX: cost of durability < consistency
{\it Durability \(<<\) Consistency:} The \(1.15\times\) overhead of
Strong Consistency compared to Strong Consistency, No Fault Tolerance for
100K files is negligible. It suggests that the overhead of consistency is much
larger than the overhead of durability. This conclusion should be stronger as
we scale the number of files because the cost of streaming the journal into the
object store is constant. We omit the same analysis for Weak Consistency
because the runtimes are so short that the normalized slowdowns are misleading.

@@

\noindent\textbf{Takeaway}: Cudele shows the true benefit of eventual
consistency, where we see over a \(100\times\) slowdown for achieving strong
consistency, in the worst case.

>>>>

@@

\subsection{Microbenchmarks}
\label{sec:microbenchmarks}
\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/composable-mechanisms.png}
\caption{ [\href{https://...}{source}] Microbenchmark: performance of each
mechanism (left) and building consistency/durability guarantees (right) for
100K files on a single client. Results are normalized to the runtime of writing
files creates to the client's in-memory journal.
\label{fig:composable-mechanisms}}
\end{figure}

@@

Figure~\ref{fig:composable-mechanisms} shows the runtime of the Cudele
mechanisms for a single client creating files in the same directory, normalized
to the time it takes to write 100K file create updates to the client's
in-memory journal ({\it i.e.} the ``Append Client Journal" mechanism).
``Stream" is an approximation of the overhead and is calculated by subtracting
the runtime of the job with the journal turned off from the runtime with the
journal turned on.  100K is the maximum recommended size of a directory in
CephFS; preliminary experiments with larger directory sizes show memory
problems.

{\it Poorly Scaling Data Structures:} Despite doing the same amount of work,
mechanisms that rely on poorly scaling data structures have large slowdowns for
the larger number of creates. For example, ``RPCs" which relies on the internal
CephFS directory structures has a \(90\times\) slowdown for 100K files. It is a
well-known problem that directory data structures do not scale when creating
files in the same directory~\cite{ren:sc2014-indexfs} and any mechanism that
uses these data structures will experience similar slowdowns. Other mechanisms
that write events to a journal ({\it e.g.} the persists, ``Volatile Apply")
experience a much less drastic slowdown because the journal data structure does
not need to be scanned for every operation. Events are written to the end of
the journal without even checking the validity ({\it e.g.}, if the file already
exists for a create), which is another form of relaxed consistency because the
file system assumes the application has resolved conflicting updates in a
different way.

@@

% persist vs. save: one disk vs. many
{\it Parallelism of the Object Store:} Comparing ``Local" and ``Global
persist" demonstrates the bandwidth advantages of storing the journal in a
distributed object store. The ``Global Persist"
performance is \(1.5\times\) faster because the object store is leveraging the
collective bandwidth of the disks in the cluster. This benefit comes from the
object store itself but should be acknowledged when making decisions for the
application; the size of the object store can help mitigate the overheads of
globally persisting metadata updates.

@@

\noindent\textbf{Takeaway}: measuring the mechanisms individually shows that
their overheads and costs can differ {\it by orders of magnitude}. Cudele gives
users the ability to quantify the performance impact of different
consistency/durability guarantees.\\

\subsection{Use Case 1: Creates in the Same Directory}
\label{sec:use-case-1}

@@

%\begin{figure}[tb]
%\centering
%\includegraphics[width=1.0\linewidth]{graphs/slowdown-strong-v-weak.png}
%\caption{ [\href{https://...}{source}] Use Case 1: the RPC per metadata update
%(strong consistency) has a large overhead compared to decoupled namespaces
%(weak consistency.)\label{fig:slowdown-strong-weak}}
%\end{figure}

The graph on the right of Figure~\ref{fig:composable-mechanisms} shows how
applications can compose mechanisms together to get the consistency/durability
guarantees they need.  We label the \(x\)-axis with systems that employ these
semantics, as described in Figure~\ref{fig:subtree-policies}.  Again, the
runtime of different semantics for subtrees in the same global namespace
normalized to the runtime of the ``Append Client Journal" mechanism (again,
just creating files in the client's in-memory journal).  We makes no guarantees
during execution of the mechanisms or when transitioning semantics -- the
semantics are guaranteed {\it once the mechanism completes}. So if servers fail
during a mechanism, metadata or data may be lost.

%% DeltaFS vs. BatchFS vs. POSIX: decoupled is faster
%% (5-7x) vs. (90-104x) slower
%% Does not scale?
%% Strong Consistency > 10X slower than Weak Consistency 
%{\it Speedups of Decoupled Namespaces:} Weak consistency uses the
%decoupled namespace strategy and shows up to a \(20\times\) speedup over the
%traditional namespaces that use RPCs. Compared to the baseline the slowdown is
%\(5-7\times\) for Strong Consistency, which emulates BatchFS and
%\(90-104\times\) for Weak Consistency, which emulates DeltaFS.

{\it Durability \(<<\) Consistency:} The performance of these semantics
suggests that the overhead of consistency is much larger than the overhead of
durability. This conclusion should be stronger as we scale the number of files
because the cost of streaming the journal into the object store is constant.

@@

\noindent\textbf{Takeaway}: we confirm the performance benefits of other
well-established research systems but, more importantly, we show that the
Cudele mechanisms we propose are useful for building evaluating different
consistency/durability semantics.
